\pkg{partykit}: A Toolbox for Recursive Partytioning

### 2009-02-25 pkg/inst/slides/DSC-2009_abstract.tex
new DSC abstract
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@128 255f4249-2263-4417-b1ea-8498779e27a7

\usepackage{url,a4wide}
\usepackage[authoryear,round]{natbib}

@@

\begin{keywords}
Regression Trees, Visualization, CTree, CHAID, Weka, PMML.
\end{keywords}

@@

To overcome these difficulties, the \pkg{partykit} package \citep{partykit:partykit} offers a 
unified representation of tree objects along with \code{predict()}, 
\code{print()}, and \code{plot()} methods. Trees are represented through 
a new flexible class \class{party} which can, in principle, capture
all trees mentioned above but can also accomodate multi-way or functional
splits, as well as complex models in (leaf) nodes. The package is currently
under development at R-Forge but already provides conversion methods for
trees of classes \class{rpart}, \class{J48}, and \class{pmmlTreeModel}
as well as a re-implementation of conditional inference trees \citep{partykit:Hothorn+Hornik+Zeileis:2006}.

In our presentation, we will only sketch details of these classes and 
corresponding methods and focus on applications of the toolkit including
extended visualizations for \class{rpart} or \class{J48} objects, fast predictions
on millions of new observations, and a new implementation of the classical CHAID
algorithm.

>>>>

\usepackage{url,a4wide}
\usepackage[authoryear,round]{natbib}
\topmargin-1.5cm
\textheight28cm

@@

\begin{keywords}
Regression Trees, Visualization, CTree, CHAID, MOB, Weka, PMML.
\end{keywords}

@@

To overcome these difficulties, the \pkg{partykit} package \citep{partykit:partykit} offers a 
unified representation of tree objects along with \code{predict()}, 
\code{print()}, and \code{plot()} methods. Trees are represented through 
a new flexible class \class{party} comprising essentially a recursive list of \class{partynode}
objects along with \class{partysplit} information. Additionally, further
information about the underlying data as well as the associated model fit
can be stored and accessed. Therefore, the \class{party} class can capture
all trees mentioned above but can also accomodate multi-way or functional
splits, as well as complex models in (leaf) nodes. The package is currently
under development at \proglang{R}-Forge but already provides conversion methods for
trees of classes \class{rpart}, \class{J48}, and \class{pmmlTreeModel}
as well as a re-implementation of conditional inference trees \citep{partykit:Hothorn+Hornik+Zeileis:2006}.

In our presentation, we discuss the design of the new \class{party} class
and its methods and illustrate how it can be utilized to interface other classes such
as \class{rpart} or \class{J48}, obtain new implementations of existing algorithms
such as CHAID or re-implement techniques such as model-based recursive partitioning
\citep[MOB,][]{partykit:Zeileis+Hothorn+Hornik:2008}.
